Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-05-23 review/answer_to_review_2.md

TODO

> Page 3, Column 1, Lines 2-6. Great!

> Page 3, Column 2, Line 59. ‘the region are circular’ Why this shape if it causes overlap? Why not hexagons?

This is true. I added a sentence to point this out. For this paper I will use the established regions, because changing them at this point would render the area discussions useless. In the future more data might be available and it should be possible to establish a lot more fine grained, hexagonal or rectangular region grid.

### 2019-05-23 review/answer_to_review_2.md

> Page 2, Column 1, Line 29. ‘simplify survival’ → increase?

Rephrased.

> Page 2, Column 1, Line 42. ‘seemlingly random’  This is one of those tricky phrasing that has different meaning depending on the readership. ‘Random’ to me almost equals to unbiased transmission with drift, and stating that it is ‘seemlingly’ reads as if in reality this is not the case. This is perfectly fine, but it is slightly at odds with the definition of ‘style’ and the implicit assumption of neutrality. I would consider rephrasing, just to avoid potential misunderstandings.

You're right. I thought a lot about this and finally decided to simply remove the term ‘seemlingly random’. In my opinion the binary distinction between style and function reaches its limit with burial traditions. In many cultural contexts, death and funerals are strongly reflected. Much more thought is given to this than to patterns on pots. The simulation paper will have to look at this difference more carefully, because there the neutrality is an even more important assumption.

### 2019-05-23 article/01_Introduction.Rmd
phrasing
seemingly random: neutrality

*Evolutionary archaeology*, the branch of archaeology that explicitly adopted Cultural evolution theory, established an important distinction of cultural behaviour in *function* and *style* [@dunnell1978style] which is relevant for burial traditions. Some types of human behaviour increase well-being and simplify survival, like specific hunting techniques, superior tools or sowing more fruitful crops. Without resorting to the inappropriate simplifications of Evolutionism, their prevalence generally happens to increase over time. On the other hand, some behaviours are not related to survival and reproductive capacity, like e.g. ceramic decorations, traditional costume fashion or jewellery design. Despite or because their seemingly subordinate importance, these characteristics often pass through a breathtakingly fast development. Burial traditions can be described as a special form of these *stylistic traits*. Special because of their strong dependence on religious and spiritual beliefs and their connection with the emotionally stirring topic of death, but still subject to sometimes rapid and seemingly random fashion changes.

>>>>

*Evolutionary archaeology*, the branch of archaeology that explicitly adopted Cultural evolution theory, established an important distinction of cultural behaviour in *function* and *style* [@dunnell1978style] which is relevant for burial traditions. Some types of human behaviour increase the chances of survival, like specific hunting techniques, superior tools or sowing more fruitful crops. Without resorting to the inappropriate simplifications of Evolutionism, their prevalence generally happens to increase over time. On the other hand, some behaviours are not related to survival and reproductive capacity, like e.g. ceramic decorations, traditional costume fashion or jewellery design. Despite or because their seemingly subordinate importance, these characteristics often pass through a breathtakingly fast development. Burial traditions can be described as a special form of these *stylistic traits*. Special because of their strong dependence on religious and spiritual beliefs and their connection with the emotionally stirring topic of death, but still subject to sometimes rapid fashion changes.
